TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-15 paper/draft.tex
selection before/after caption

\begin{figure}[ht]
\gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
          \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
\gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\caption{Final sample selection with 10,311 M dwarfs based on criteria described in Section \ref{subsec:test_selection}; temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases with increasing absolute magnitude as expected. Deviations from these gradients seen at the upper slice of the main sequence is due to binaries. \label{fig:safe_selection}}
\end{figure}

>>>>

\begin{figure}[ht]
% \gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
%           \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
% \gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\plottwo{figures/cmd_teff_full.png}{figures/cmd_teff_safe.png}
\plottwo{figures/cmd_feh_full.png}{figures/cmd_feh_safe.png}
\plottwo{figures/cmd_spt_full.png}{figures/cmd_spt_safe.png}
\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 10,311 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, binaries, and K dwarfs). Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases with increasing absolute magnitude as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence. \label{fig:safe_selection}}
\end{figure}
